---
title: "Introduction"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

When creating R markdown websites, I often find myself wanting to organise content into a nice-looking grid of links. For example, in a recent project I wanted something like this:

```{r, echo=FALSE}
library(bs4cards)
slides <- list(
  
  card(
    title = "Starting R markdown",
    image = "https://slides.djnavarro.net/index_img/starting-rmarkdown.png",
    link = "https://slides.djnavarro.net/starting-rmarkdown",
    text = "An introduction to R markdown. The target audience is a novice R user with no previous experience with markdown."
  ),

  card(
    title = "Starting ggplot2",
    image = "https://slides.djnavarro.net/index_img/starting-ggplot2.png",
    link = "https://slides.djnavarro.net/starting-ggplot2",
    text = "An introduction to ggplot2. The target audience is a novice user with no previous experience with R or ggplot2."
  ),

  card(
    title = "Starting programming",
    image = "https://slides.djnavarro.net/index_img/starting-programming.png",
    link = "https://slides.djnavarro.net/starting-programming",
    text = "This is primarily a tutorial on making generative art in R, but in doing so introduces core programming constructs and data structures. It is assumed the user has some previous experience with ggplot2."
  )
)

card_group(slides)
```

The goal of bs4cards is to his task a little easier inside an R markdown document or website. 


## Enabling bootstrap 4

The first step in using the package is to make sure that your R markdown document uses version 4 of bootstrap: the `bs4cards` package takes its name from the "cards" system introduced in bootstrap version 4, and will not work properly if used in R markdown documents that rely on bootstrap version 3. To ensure that you are using bootstrap 4, you need to edit the YAML header for your document to specify which version of bootstrap you want to use. For example, here is the relevant section of YAML you might use in a simple R markdown site 

```
output:
  html_document:
    theme:
      version: 4
```

This overrides the R markdown defaults to ensure that the output is built using [bootstrap 4.5](https://getbootstrap.com/docs/4.5/getting-started/introduction/). To enable bootstrap 4 in a pkgdown site such as this one, edit the `_pkgdown.yml` file to include the following

```
template:
  bootstrap: 4
```

You may need to update to the development version of pkgdown to make this work.


## Building bootstrap cards

The main function in bs4cards is the `card()` function. To create a minimal text-only card, call the `card()` function specifying the `title` and `text` arguments:

```{r}
library(bs4cards)

card(
  title = "A bootstrap card", 
  text = "This is a minimal bootstrap 4 card containing title and text"
)
```


In most cases you'll also want to add an image to the card using the `image` argument. This argument specifies the path to the image file. For the purposes of this example I'll set image paths using links to [placekitten.com](https://placekitten.com):

```{r}
card(
  title = "A kitten card",
  image = "https://placekitten.com/300/200",
  text = "The image at the top of this card is from placekitten.com. It's very cute"
)
```

Images are placed at the top of the card by default, but can be moved to the bottom by setting `image_align = "bottom"`:

```{r}
card(
  title = "A kitten card",
  image = "https://placekitten.com/300/200",
  text = "The image at the bottom of this card is from placekitten.com. It's still cute",
  image_align = "bottom"
)
```

In most cases you'll want cards to be associated with a link, which is set by specifying the `link` argument to `card()`. This will convert both the card title and image to links:

```{r}
card(
  title = "Placekittens",
  image = "https://placekitten.com/300/200",
  text = "The image at the top of this card is from placekitten.com. It's very cute",
  link = "https://placekitten.com"
)
```



## Card grids


```{r}
kitty_list <- list(
  sample_card(), sample_card(), sample_card(), sample_card(),
  sample_card(), sample_card(), sample_card(), sample_card()
)

card_group(kitty_list)
```


## Headers and footers


```{r}
kitties_with_footers <- list(
  sample_card(footer = "Kitten A"), 
  sample_card(footer = "Kitten B"), 
  sample_card(footer = "Kitten C")
) 

card_group(kitties_with_footers)
```


```{r}
kitties_with_headers <- list(
  sample_card(header = "Kitten A"), 
  sample_card(header = "Kitten B"), 
  sample_card(header = "Kitten C")
)

card_group(kitties_with_headers)
```


## Customising card width


```{r}
card(
  title = "My First Card",
  image = "https://placekitten.com/300/200",
  text = "The image above is from placekitten.com. It is extremely cute.",
  width = bs_col(medium = 4) 
)

card(
  title = "My First Card",
  image = "https://placekitten.com/300/200",
  text = "The image above is from placekitten.com. It is extremely cute.",
  width = bs_col(medium = 6) 
)

card(
  title = "My First Card",
  image = "https://placekitten.com/300/200",
  text = "The image above is from placekitten.com. It is extremely cute.",
  width = bs_col(large = 6) 
)
```



