---
title: "Borders"
description: >
  Controlling the colour, width, and rounding applied to the card borders
---

```{r, include = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tibble)
library(bs4cards)
```

The colour and width of card borders are customisable, as is the amount of rounding on the card borders. 

## Border width

To remove the borders entirely set `border_width = 0`:

```{r}
galleries[1:3, ] %>% 
  cards(
    title = long_name,
    image = image_url, 
    border_width = 0
  )
```

For thick borders, set `border_width = 5`:

```{r}
galleries[1:3, ] %>% 
  cards(
    title = long_name,
    image = image_url, 
    border_width = 5
  )
```


## Border colour

The colour of the card borders is specified using `border_colour` and recognises any valid colour string recognised by CSS. The input can either be a single colour, but you can also pass a vector as input assigning each card a different border colour:

```{r}
galleries[1:3, ] %>% 
  cards(
    title = long_name,
    image = image_url, 
    border_width = 2,
    border_colour = c("#8b0000", "black", "#0b0b80")
  )
```


## Border radius

The `border_radius` argument is used to control the degree of rounding of the card borders, and should be an integer between 0 and 5. At `border_radius = 0` the cards are perfectly rectangular, with no rounding at all:

```{r}
galleries[1:3, ] %>% 
  cards(
    title = long_name,
    image = image_url, 
    border_radius = 0,
  )
```

At the roundest setting `border_radius = 5` produces noticeably rounded rectangles:

```{r}
galleries[1:3, ] %>% 
  cards(
    title = long_name,
    image = image_url, 
    border_radius = 5,
  )
```


## Additional customisation

Additional border customisation is possible, by passing character strings for `border_width` and `border_width`. When character input is used, the `cards()` function passes the input directly to the CSS. For example, you can create cards with circular images and very thick borders like this:

```{r}
galleries[1:3, ] %>% 
  cards(
    image = image_url, 
    border_colour = "#dddddd",
    border_width = "20px",
    border_radius = "20rem",
  )
```



