---
title: "Colours"
description: >
  Controlling the colour of the card label
---

```{r, include = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tibble)
library(bs4cards)
```


By default the `label_colour` argument is set to `NULL`, and is interpreted as a CSS value of `"inherit"`. However, you can override this and set the card label colour manually. The `label_colour` argument will accept any valid colour string recognised by R. The input can either be a single colour or a vector assigning each card a different label colour:

```{r}
galleries[1:3, ] %>% 
  cards(
    title = long_name,
    text = blurb,
    link = gallery_url,
    image = image_url,
    label_colour = c("#d6cadd", "antiquewhite", "#c4d8e2")
  )
```


For inset layouts, the colour needs to be partly transparent if you want the image underneath to show through:

```{r}
galleries[1:3, ] %>% 
  cards(
    title = long_name,
    text = blurb,
    link = gallery_url,
    image = image_url,
    layout = "inset-bottom",
    label_colour = c("#d6caddaa", "#ffffffaa", "#c4d8e2aa"),
    breakpoint = 5
  )
```



