---
title: "Customising cards"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bs4cards)
```


The bs4cards package comes with a data set `galleries`:

```{r}
galleries
```

Define some convenience functions that specify URLs for the image thumbnail and the target location for a link:

```{r}
locate_thumbnail <- function(x) {
  paste0("https://bs4cards.djnavarro.net/image/", x, ".jpg")
} 
locate_gallery <- function(x) {
  paste0("https://art.djnavarro.net/gallery/", x)
}
```

Off we go: 

```{r}
galleries %>% 
  cards(
    title = long_name,
    text = date,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name)
  )
```


## Choosing a layout

### Vertical layouts

The bs4cards package supports six different layouts: two "vertical" layouts, two "horizontal" layouts, and two "inset" layouts. If you want vertically oriented cards, set `layout = "label-above"` or `layout = "label-below"` (the default) to create the cards:

```{r}
galleries %>% 
  cards(
    title = long_name,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name),
    footer = paste("posted on", date),
    width = "wide",
    layout = "label-above"
  )
```


```{r}
galleries %>% 
  cards(
    title = long_name,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name),
    text = blurb,
    footer = paste("posted on", date),
    width = "wide",
    layout = "label-below"
  )
```


### Horizontal layouts

To set horizontal layouts, set `layout = "label-left"` or `layout = "label-right"`:

```{r}
galleries %>% 
  cards(
    title = long_name,
    text = blurb,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name),
    width = "very-wide",
    layout = "label-left"
  )
```


```{r}
galleries %>% 
  cards(
    title = long_name,
    text = blurb,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name),
    width = "very-wide",
    footer = paste("posted on", date),
    layout = "label-right",
    breakpoint = 7/12
  )
```



### Inset layouts

The inset layouts place the "label" part of the card as a floating overlay on top of the image. The overlay can appear at the top or the bottom, depending on whether `layout = "inset-top"` or `layout = "inset-bottom"`:

```{r}
galleries %>% 
  cards(
    title = long_name,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name),
    width = "wide",
    layout = "inset-top", 
    colour = "#ffffffcc"
  )
```


```{r}
galleries %>% 
  cards(
    title = long_name,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name),
    width = "wide",
    layout = "inset-bottom", 
    colour = "#ffffffcc", 
    rounding = 0
  )
```


```{r}
galleries %>% 
  cards(
    title = long_name,
    footer = blurb,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name),
    width = "wide",
    layout = "inset-bottom", 
    colour = "#ffffffcc"
  )
```


```{r}
galleries %>% 
  cards(
    title = long_name,
    text = blurb,
    footer = date,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name),
    width = "wide",
    layout = "inset-bottom", 
    breakpoint = .5,
    colour = "#ffffffcc"
  )
```


## Tags

The `tags` argument can be used to assign each card to a set of tags, and adds toggle buttons at the top of the card list that the user can do to display only those cards possessing the tag in question. The tags should be a single string, with spaces separating each tag. In the `galleries` data, the `paintbrushes` variable contains a list of some of the packages that were used in generating each generative art system. It's generally a good idea to have one tag that is possessed by all of the cards. The bs4cards package doesn't enforce this, but it's easy to do as illustrated below:

```{r}
galleries %>% 
  cards(
    title = long_name,
    text = blurb,
    link = locate_gallery(short_name),
    image = locate_thumbnail(short_name),
    tags = paste("all", paintbrushes),
    width = "very-wide",
    footer = paintbrushes,
    layout = "label-right",
    breakpoint = 7/12
  )
```

<br><br><br>
<br><br><br>
<br><br><br>
<br><br><br>
<br><br><br>
<br><br><br>
<br><br><br>
<br><br><br>
