---
title: "Card layouts"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tibble)
```

```{r setup}
library(bs4cards)
```



## Layout of a card

The bs4cards package supports a total eight different `layout` formats. First, there are two vertical layouts and two horizontal layouts:

- Setting `layout = "label-below"` places the label below the image (the default)
- Setting `layout = "label-above"` places the label above the image
- Setting `layout = "label-left"` places the label to the left of the image
- Setting `layout = "label-right"` places the label to the right of the image

Some examples:

```{r}
galleries %>% 
  cards(
    title = long_name,
    link = gallery_url,
    image = image_url,
    layout = "label-above"
  )
```

```{r}
galleries %>% 
  cards(
    title = long_name,
    link = gallery_url,
    image = image_url,
    text = blurb,
    layout = "label-right",
    width = 4
  )
```

(Notice that I set `width = 4` for the horizontal card. Horizontal layouts tend to need more horizontal space, especially when the label includes text as well as a title. The width of the cards is controlled by the `width` argument, and I'll talk more about it later)

In addition there are two "singleton" layouts:

- Setting `layout = "label-only"` includes a label but no image
- Setting `layout = "image-only"` includes an image but no label

As a convenience, the `cards()` function will detect when the user has not specified a label (or image) and will choose the appropriate layout automatically:

```{r}
galleries %>% 
  cards(
    link = gallery_url,
    image = image_url
  )
```


Finally there are two "inset" layouts, in which the label is displayed as an overlay on top of the image. These two layouts are experimental, and I wouldn't advise using them just yet. But if you want to try...

- Setting `layout = "inset-top"` places the label at the top of the image
- Setting `layout = "inset-bottom"` places the label at the bottom of the image

```{r}
galleries %>% 
  cards(
    title = long_name,
    text = blurb,
    link = gallery_url,
    image = image_url,
    layout = "inset-top"
  )
```
